Building a Probabilistic Model with Deep Neural Networks for Camera Geo-Calibration

### 2018-06-30 chapters/introduction/introduction.tex
minor changes

As one of the primary vision tasks, camera calibration plays an
important role in many applications like indoor layout estimation and
image mensuration. 
In the camera pin-hole model, camera calibration parameters consist of
the camera intrinsics and the extrinsic. The intrinsic parameters of
a camera encode information of the camera itself such as focal length,
principal point \etc; the extrinsic parameters are referred to as the
external states of the camera, such as the camera poses and
offset/location under some coordinate system. Specifically,
camera geo-calibration consider the camera locations in the geographic
coordinates.
In this work, our study mainly focus on the extrinsic like camera pose
and the geo-orientation/geo-localization of the camera.

In current work of camera calibration, most algorithms are
deterministic, which means they output fixed solutions. Applications
that takes probabilistic inputs (especially for those which use
graphic model) don't like it. To address this, we propose to build
probabilistic models for camera geo-calibration using deep neural
networks.

A complete geo-calibration detect both camera intrinsic (focal length,
principal points \etc) and extrinsic parameters, which includes camera
roll, pitch angles, geographic orientation and geographic locations.
In our work, we first build a probabilistic model to detect multiple
geo-calibration parameters jointly. Our algorithm construct a set of
constraint functions to measure the fitness between the
geo-calibration parameters and the observations. An energy function
is constructed with these constraint functions. Thus each point in the
solution space forebear a energy score (proportional to the
probability at that point). We then use graphic model approach to
sample these point in the space.

>>>>

As one of the primary vision tasks, camera calibration plays an
important role in many applications like autonomous driving, indoor
layout estimation and image mensuration. 
In the camera pin-hole model, the projection from scene to the image
frame are determined by camera intrinsic and extrinsic parameters. 
The intrinsic parameters describe the information of camera
itself such as focal length, principal point \etc; 
The extrinsic parameters describe the external states of the
camera, such as the camera poses and translation under some
coordinate system.
Some applications like GIS and geo-localization are more interested in
calibrating the camera under geographic coordinates, namely knowing
the camera pose with respect to the ground reference frame (\ie ENU)
and camera location in geographic coordinates. We refer to such
calibration as \textbf{geo-calibration}.
In this work, our study mainly focuses on estimating geo-calibration
extrinsic parameters like camera pose and the
geo-orientation/geo-localization of the camera.

In current work of camera calibration, most algorithms are
deterministic, which means they output fixed solutions. Deterministic
systems may seem straight-forward but they also forebear the following
drawbacks: 1) Deterministic systems can not handle uncertainties which
are commonly encountered in the real world problems.  2) Deterministic
systems are not friendly to applications developed with graphic models
that are interfaced with their outputs.
To address these drawbacks, We propose to build probabilistic
models for camera geo-calibration.

A complete geo-calibration detects both camera intrinsic (focal length,
principal points \etc) and extrinsic parameters, which includes camera
roll, pitch angles, geographic orientation and geographic locations.
In our work, we first build a probabilistic model to detect multiple
geo-calibration parameters jointly. Our algorithm construct a set of
constraint functions to measure the fitness between the
geo-calibration parameters and the observations. An energy function
is constructed with these constraint functions. Thus each point in the
solution space forebear a energy score (proportional to the
probability at that point). We then use graphic model approach to
sample these point in the space.
